Informing policy via dynamic models: Cholera in Haiti

### 2024-01-23 ms.Rnw
Incorporated H1 profile results into the manuscript

# Setting algorithmic hyper-parameters based on RUN_LEVEL.
#
#                    RUN_LEVEL =  1,   2,    3
N_PARAMS   <- switch(RUN_LEVEL,  10,  20,  nrow(h1LeeStartsEpi))  # Number of parameters to sample
N_LEE_SIMS <- switch(RUN_LEVEL,  10,  20,   20)  # Number of simulations per parameter
NP_EVAL    <- switch(RUN_LEVEL,  50, 200, 2000)  # Number of particles used to evaluate the likelihood
NREPS_EVAL <- switch(RUN_LEVEL,   3,   5,   36)  # Number of replicates of likelihood evaluation.

@@

# Compute the run_level_<RUN_LEVEL> results and save them.
lee_epi_ll <- readRDS("model1/run_level_3/lee1_epi_evals.rds")
# lee_epi_ll <- bake(
#   file = paste0("model1/", rl_dir, "lee1_epi_evals.rds"), {
#
#     # Randomly sample from starting params used by Lee et al (2020).
#     # If RUN_LEVEL == 3, all starting parameters are used.
#     which_params <- sample(
#       1:nrow(h1LeeStartsEpi),
#       size = N_PARAMS,
#       replace = FALSE
#     )
#     epi_params <- h1LeeStartsEpi[which_params, ]
#
#     # Create data.frame to save results
#     lee_epi_ll <- data.frame(
#       "pfLL" = NA_real_,
#       "pfse" = NA_real_,
#       "parid" = epi_params$parid
#     )
#
#     for (j in 1:nrow(lee_epi_ll)) {
#       # Get parameters of interest
#       pf_params <- epi_params[j, -1][names(coef(h1_epi))]
#
#       # make results reproducible
#       registerDoRNG((j * 687383921) %% 7919)
#
#       # Calculate log likelihoods
#       ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
#         logLik(pfilter(h1_epi, params = pf_params, Np = NP_EVAL))
#       }
#       lee_epi_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]  # Log-lik
#       lee_epi_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]  # SE
#     }
#
#     lee_epi_ll
#   }
# )

@@

lee_end_ll <- readRDS("model1/run_level_3/lee1_end_evals.rds")
# lee_end_ll <- bake(
#   file = paste0("model1/", rl_dir, "lee1_end_evals.rds"), {
#
#     end_params <- h1LeeStartsEnd[h1LeeStartsEnd$parid %in% lee_epi_ll$parid, ]
#
#     # Create data.frame to save results
#     lee_end_ll <- data.frame(
#       "pfLL" = NA_real_,
#       "pfse" = NA_real_,
#       'parid' = end_params$parid
#     )
#
#     # Perform particle filter to get likelihood estimates
#     for (j in 1:nrow(lee_end_ll)) {
#       # Get parameters of interest
#       pf_params <- end_params[j, ][names(coef(h1_end))]
#
#       # make results reproducible
#       registerDoRNG((j * 687383921) %% 7919)
#
#       # Calculate log likelihoods
#       ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
#         logLik(pfilter(h1_end, params = pf_params, Np = NP_EVAL))
#       }
#
#       lee_end_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]
#       lee_end_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]
#     }
#
#     lee_end_ll
#   }
# )

# Combine epidemic and endemic likelihoods by parid to get the likelihood of
# the complete model.
mod1_all_likes <- dplyr::inner_join(
  x = lee_epi_ll,
  y = lee_end_ll,
  by = "parid"
  ) %>%
  dplyr::mutate(
    joint_ll = pfLL.x + pfLL.y
  )

@@

rm(
  lee_end_ll, lee_epi_ll, h1_end, h1_epi, i, mod1_all_likes,
  N_LEE_SIMS, N_PARAMS, NP_EVAL, NREPS_EVAL, end_params, epi_params,
  pf_params, j, ll_evals, which_params
)
gc()
@

@@

<<FitModel1, echo=FALSE, message=FALSE, include=FALSE>>=

@@

# Check RUN_LEVEL, and set hyper-parameters to IF2 and pfilter accordingly.
#                      RUN_LEVEL =    1,    2,      3
NP_H1        <- switch(RUN_LEVEL,   100, 1000,   2000)
NMIF_H1      <- switch(RUN_LEVEL,    10,   50,    200)
NUM_TREND    <- switch(RUN_LEVEL,     5,   10,     90)
NPROF        <- switch(RUN_LEVEL,     4,    4,     24)
NP_EVAL      <- switch(RUN_LEVEL,   200, 1000,   5000)
NREPS_EVAL   <- switch(RUN_LEVEL, cores,   20,  cores)

# Create the <RUN_LEVEL> version of the results and save them.
h1_MIF <- readRDS('model1/run_level_3/haiti1_fit.rds')

# h1_MIF <- bake(
#   file = paste0("model1/", rl_dir, "haiti1_fit.rds"), {
#     fit_haiti1(  # haitipkg function used to fit Model 1
#       NP = NP_H1,
#       NMIF = NMIF_H1,
#       NUM_TREND = NUM_TREND,
#       NPROF = NPROF,
#       NREPS_EVAL = NREPS_EVAL,
#       NP_EVAL = NP_EVAL
#     )
#   }
# )

# The result is a data.frame containing many parameter values and their
# corresponding likelihood evaluation. To perform a likelihood profile,
# we calculate the maximum likelihood for each value of betat.
h1_prof_res <- h1_MIF %>%
  group_by(betat) %>%
  summarize(logLik = max(ll))

mcap_results <- pomp::mcap(h1_prof_res$logLik, h1_prof_res$betat, span = 1)

# Get the best set of parameters from MIF2 search.
p1 <- h1_MIF %>%
  filter(ll == max(ll)) %>%
  select(-ll, -ll.se) %>%
  unlist()

# Save the likelihood of the best parameters, for use later.
mod1_ll <- h1_MIF %>%
  filter(ll == max(ll)) %>%
  select(ll) %>%
  unlist()

# Just a bit of tidying up: removing parameters that we won't use again.
rm(NP_H1, NMIF_H1, NUM_TREND, NPROF, NREPS_EVAL, NP_EVAL, h1_MIF)
gc()

@@

@@

<<table-input,echo=FALSE,eval=T, include=FALSE, message=FALSE>>=

@@

\begin{figure}[!h]
\centering
<<Beta_trend_Figure, fig.height=2.4, fig.width=3.6, fig.align='center'>>=
ggplot() +
  geom_point(data = h1_prof_res, aes(x = betat, y = logLik)) +
  geom_line(data = mcap_results$fit, aes(x = parameter, y = smoothed), col = 'blue') +
  geom_vline(xintercept = mcap_results$ci[1], linetype = 'dashed') +
  geom_vline(xintercept = mcap_results$ci[2], linetype = 'dashed') +
  geom_vline(xintercept = mcap_results$mle, col = 'blue') +
  labs(x = "Linear Trend in Transmission", y = 'Log Likelihood') +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10))
@
\caption{\label{fig:betat}
{\figTitle Confidence interval for linear trend in transmission.}
Monte Carlo adjusted profile of $\transmissionTrend$ for Model~1.
The blue curve is the profile, the blue line indicates the MLE, and the dashed lines indicate the $95\%$ confidence interval.
}
\end{figure}

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S0_results <- readRDS("model1/run_level_3/S0_sims.rds")
# h1_S0_results <- bake(
#   file = paste0("model1/", rl_dir, "S0_sims.rds"), {
#
#     # Create the model
#     s0 <- haiti1_joint(vacscen = 'id0')
#
#     # Load coefficients
#     coef(s0) <- p1
#
#     # Get samples from filtering distribution
#     s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s0_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S0_sims <- project_from_filter(mod = s0, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
#     results$mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S2_results <- readRDS("model1/run_level_3/S2_sims.rds")
# h1_S2_results <- bake(
#   file = paste0('model1/', rl_dir, 'S2_sims.rds'), {
#
#     # Create the model
#     s2 <- haiti1_joint(vacscen = "id2")
#
#     # Set model parameters that need to be adjusted
#     depts <- 2
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s2) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s2_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
#     results$mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S4_results <- readRDS("model1/run_level_3/S4_sims.rds")
# h1_S4_results <- bake(
#   file = paste0('model1/', rl_dir, 'S4_sims.rds'), {
#
#     # Create the model
#     s4 <- haiti1_joint(vacscen = "id4")
#
#     # Set model parameters that need to be adjusted
#     depts <- 3
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s4) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s4_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
#     results$mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S3_results <- readRDS("model1/run_level_3/S3_sims.rds")
# h1_S3_results <- bake(
#   file = paste0('model1/', rl_dir, 'S3_sims.rds'), {
#
#     # Create the model
#     s3 <- haiti1_joint(vacscen = "id3")
#
#     # Set model parameters that need to be adjusted
#     depts <- 10
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s3) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s3_pf <- pfilter(s3, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s3_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V3_sims <- agg_mod1_sims(h1_S3_sims)
#     results$mod1_V3_probs <- get_elimProbs(h1_S3_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S1_results <- readRDS("model1/run_level_3/S1_sims.rds")
# h1_S1_results <- bake(
#   file = paste0('model1/', rl_dir, 'S1_sims.rds'), {
#
#     # Create the model
#     s1 <- haiti1_joint(vacscen = "id1")
#
#     # Set model parameters that need to be adjusted
#     depts <- 10
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s1) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s1_pf <- pfilter(s1, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s1_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S1_sims <- project_from_filter(mod = s1, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V4_sims <- agg_mod1_sims(h1_S1_sims)
#     results$mod1_V4_probs <- get_elimProbs(h1_S1_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )
@

>>>>

# Setting algorithmic hyper-parameters based on RUN_LEVEL.
#
#                    RUN_LEVEL =  1,   2,    3
N_PARAMS   <- switch(RUN_LEVEL,   5,  20,  nrow(h1LeeStartsEpi))  # Number of parameters to sample
N_LEE_SIMS <- switch(RUN_LEVEL,   5,  20,   20)  # Number of simulations per parameter
NP_EVAL    <- switch(RUN_LEVEL,  50, 200, 2000)  # Number of particles used to evaluate the likelihood
NREPS_EVAL <- switch(RUN_LEVEL,   2,   5,   36)  # Number of replicates of likelihood evaluation.

@@

if (RUN_LEVEL == 1 && file.exists('model1/run_level_3/lee1_epi_evals.rds')) {

  # If RUN_LEVEL == 1, and RUN_LEVEL == 3 results exist, just load the RL3
  # results.
  lee_epi_ll <- readRDS("model1/run_level_3/lee1_epi_evals.rds")
} else {

  # Compute the run_level_<RUN_LEVEL> results and save them, or simply load
  # the results if the bake load conditions are met.
  lee_epi_ll <- bake(
    file = paste0("model1/", rl_dir, "lee1_epi_evals.rds"), {

      # Randomly sample from starting params used by Lee et al (2020).
      # If RUN_LEVEL == 3, all starting parameters are used.
      which_params <- sample(
        1:nrow(h1LeeStartsEpi),
        size = N_PARAMS,
        replace = FALSE
      )
      epi_params <- h1LeeStartsEpi[which_params, ]

      # Create data.frame to save results
      lee_epi_ll <- data.frame(
        "pfLL" = NA_real_,
        "pfse" = NA_real_,
        "parid" = epi_params$parid
      )

      for (j in 1:nrow(lee_epi_ll)) {
        # Get parameters of interest
        pf_params <- epi_params[j, -1][names(coef(h1_epi))]

        # make results reproducible
        registerDoRNG((j * 687383921) %% 7919)

        # Calculate log likelihoods
        ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
          logLik(pfilter(h1_epi, params = pf_params, Np = NP_EVAL))
        }
        lee_epi_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]  # Log-lik
        lee_epi_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]  # SE
      }

      lee_epi_ll
    }
  )
}

@@

if (RUN_LEVEL == 1 && file.exists('model1/run_level_3/lee1_end_evals.rds')) {

  # If RUN_LEVEL == 1, and RUN_LEVEL == 3 results exist, just load the RL3
  # results.
  lee_end_ll <- readRDS("model1/run_level_3/lee1_end_evals.rds")
} else {

  # Compute the run_level_<RUN_LEVEL> results and save them, or simply load
  # the results if the bake load conditions are met.
  lee_end_ll <- bake(
    file = paste0("model1/", rl_dir, "lee1_end_evals.rds"), {

      end_params <- h1LeeStartsEnd[h1LeeStartsEnd$parid %in% lee_epi_ll$parid, ]

      # Create data.frame to save results
      lee_end_ll <- data.frame(
        "pfLL" = NA_real_,
        "pfse" = NA_real_,
        'parid' = end_params$parid
      )

      # Perform particle filter to get likelihood estimates
      for (j in 1:nrow(lee_end_ll)) {
        # Get parameters of interest
        pf_params <- end_params[j, ][names(coef(h1_end))]

        # make results reproducible
        registerDoRNG((j * 687383921) %% 7919)

        # Calculate log likelihoods
        ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
          logLik(pfilter(h1_end, params = pf_params, Np = NP_EVAL))
        }

        lee_end_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]
        lee_end_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]
      }

      lee_end_ll
    }
  )
}

# Combine epidemic and endemic likelihoods by `parid` to get the likelihood of
# the complete model.
mod1_all_likes <- dplyr::inner_join(
  x = lee_epi_ll,
  y = lee_end_ll,
  by = "parid"
  ) %>%
  dplyr::mutate(
    joint_ll = pfLL.x + pfLL.y
  )

@@

# Doing some clean-up. The goal is that each major chunk can be run independent
# of other chunks. Removing saved objects is not entirely necessary, but can
# help new users know what objects are needed later on and which were only
# temporarily needed for each particular chunk. Here we suppress warnings
# because some of the temporary objects only exist if the `bake` code needs to
# be recomputed, and hence `rm` will throw warnings if it tries to remove
# objects that don't exist.
suppressWarnings(
  rm(
    lee_end_ll, lee_epi_ll, h1_end, h1_epi, i, mod1_all_likes,
    N_LEE_SIMS, N_PARAMS, NP_EVAL, NREPS_EVAL, end_params, epi_params,
    pf_params, j, ll_evals, which_params
  )
)
gc()  # Garbage Collection to free un-used memory
@

@@

<<LoadModel1Params, echo=FALSE, message=FALSE, include=FALSE>>=

@@

# Load the file containing profiles of Model 1 Parameters.
if (RUN_LEVEL != 3 && file.exists("model1/run_level_3/h1_profiles.rds")) {
  h1_prof <- readRDS("model1/run_level_3/h1_profiles.rds")
} else if (file.exists(paste0('model1', rl_dir, 'h1_profiles.rds'))) {
  h1_prof <- readRDS(paste0('model1', rl_dir, 'h1_profiles.rds'))
} else {
  stop(paste0("Missing file: `model1/", rl_dir, 'h1_profiles.rds`;\nThe file can be obtained by running the script `H1profile.R`'))
}

# The result is a data.frame containing many parameter values and their
# corresponding likelihood evaluation. To perform a likelihood profile,
# we calculate the maximum likelihood for each value of betat.
h1_prof_res <- h1_prof %>%
  filter(prof_var == 'betat') %>%
  group_by(betat) %>%
  summarize(logLik = max(logLik))

# TODO: This is used later in figure 2 (TODO)
mcap_results <- pomp::mcap(h1_prof_res$logLik, h1_prof_res$betat, span = 1)

# Find the set of parameters that correspond to the maximum likelihood
p1 <- h1_prof %>%
  slice_max(order_by = logLik, n = 1) %>%
  # Remove non-parameters from the data.frame (hyperparameters + likelihood)
  select(-(1:12)) %>%
  unlist()

# Save the likelihood of the best parameters, for use later.
mod1_ll <- h1_prof %>%
  slice_max(order_by = logLik, n = 1) %>%
  select(logLik) %>%
  unlist()

# Just a bit of tidying up: removing parameters that we won't use again.
rm(h1_prof)
gc()
@

@@

# TODO: Model 2

@@

<<createModelObjects,echo=FALSE,eval=TRUE, include=FALSE, message=FALSE>>=

@@

\begin{figure}[!h]
\centering
<<Beta_trend_Figure, fig.height=2.4, fig.width=3.6, fig.align='center'>>=
ggplot() +
  geom_point(data = h1_prof_res, aes(x = betat, y = logLik)) +
  geom_line(data = mcap_results$fit, aes(x = parameter, y = smoothed), col = 'blue') +
  geom_line(data = mcap_results$fit, aes(x = parameter, y = quadratic), col = 'red') +
  geom_vline(xintercept = mcap_results$ci[1], linetype = 'dashed') +
  geom_vline(xintercept = mcap_results$ci[2], linetype = 'dashed') +
  geom_vline(xintercept = mcap_results$mle, col = 'blue') +
  labs(x = "Linear Trend in Transmission", y = 'Log Likelihood') +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10))
@
\caption{\label{fig:betat}
{\figTitle Confidence interval for linear trend in transmission.}
Monte Carlo adjusted profile (MCAP) of $\transmissionTrend$ for Model~1.
The blue curve is the MCAP, the vertical blue line indicates the MLE, and the vertical dashed lines indicate the $95\%$ confidence interval.
}
\end{figure}

<<cleanUpBetatFig, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE>>=
suppressWarnings(
  rm(h1_prof_res, mcap_results)
)
gc()
@

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S0_results <- bake(
  file = paste0("model1/", rl_dir, "S0_sims.rds"), {

    # Create the model
    s0 <- haiti1_joint(vacscen = 'id0')

    # Load coefficients
    coef(s0) <- p1

    # Get samples from filtering distribution
    s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s0_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S0_sims <- project_from_filter(mod = s0, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
    results$mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S2_results <- bake(
  file = paste0('model1/', rl_dir, 'S2_sims.rds'), {

    # Create the model
    s2 <- haiti1_joint(vacscen = "id2")

    # Set model parameters that need to be adjusted
    depts <- 2
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s2) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s2_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
    results$mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S4_results <- bake(
  file = paste0('model1/', rl_dir, 'S4_sims.rds'), {

    # Create the model
    s4 <- haiti1_joint(vacscen = "id4")

    # Set model parameters that need to be adjusted
    depts <- 3
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s4) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s4_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
    results$mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S3_results <- bake(
  file = paste0('model1/', rl_dir, 'S3_sims.rds'), {

    # Create the model
    s3 <- haiti1_joint(vacscen = "id3")

    # Set model parameters that need to be adjusted
    depts <- 10
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s3) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s3_pf <- pfilter(s3, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s3_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V3_sims <- agg_mod1_sims(h1_S3_sims)
    results$mod1_V3_probs <- get_elimProbs(h1_S3_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S1_results <- bake(
  file = paste0('model1/', rl_dir, 'S1_sims.rds'), {

    # Create the model
    s1 <- haiti1_joint(vacscen = "id1")

    # Set model parameters that need to be adjusted
    depts <- 10
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s1) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s1_pf <- pfilter(s1, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s1_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S1_sims <- project_from_filter(mod = s1, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V4_sims <- agg_mod1_sims(h1_S1_sims)
    results$mod1_V4_probs <- get_elimProbs(h1_S1_sims, model = 1)

    results
  },
  timing = FALSE
)
@
